Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-05-17 doc/paper.Rmd
switch to sentence wrap for ease of merging

It is important to emphasize, however, that the overall effects of SPEI on survival and growth are more severe in fragments than continuous forest (**Fig X**).
Furthermore, the magnitude of plant responses to climatic extremes is also greater in habitat fragments ---extreme drought in dry seasons and extreme precipitation in during rainy seasons are most detrimental to growth and survival in fragments.
While intact forest and its canopy buffer populations from climatic extremes, populations in fragments - especially near edges with high contrast matrix - likely lack this protection [@didham1999;@ewers2013]. We suggest it is these climate extremes, rather than trends in average temperature, precipitation, or SPEI [@laurance2014], that that are the causal mechanism underlying reduced plant growth and survival in forest fragments.

>>>>

It is important to emphasize, however, that the overall effects of SPEI on survival and growth are more severe in fragments than continuous forest (**Fig X**).
Furthermore, the magnitude of plant responses to climatic extremes is also greater in habitat fragments ---extreme drought in dry seasons and extreme precipitation in during rainy seasons are most detrimental to growth and survival in fragments.
While intact forest and its canopy buffer populations from climatic extremes, populations in fragments - especially near edges with high contrast matrix - likely lack this protection [@didham1999; @ewers2013].
We suggest it is these climate extremes, rather than trends in average temperature, precipitation, or SPEI [@laurance2014], that that are the causal mechanism underlying reduced plant growth and survival in forest fragments.
